Whittaker Models for Real Groups

### 2024-05-29 whittaker.tex
Details about why Rossmann's lemma implies WF is a single orbit

Part~(b) is one of the main results of~\cite{vogan_bowdoin}: see \cite[Theorem ?]{vogan_bowdoin}.

Part~(c) follows from~\cite{rossmann_limit_orbits}. Update May 1: it seems the right place is Lemma B, and to go from that to the statement is a matter of chasing definitions and using the asymptotic cone. I (=AA) will have a look.

\footnote{\textcolor{red}{(AA, 2024-V-1) : TODO -- find the right references, I tried but quickly got lost...}}

>>>>

Part~(b) is one of the main results of~\cite{vogan_bowdoin}: see \cite[Theorem ?]{vogan_bowdoin}.\footnote{\textcolor{red}{(AA, 2024-V-1) : TODO -- find the right references, I tried but quickly got lost...}}

Part~(c) follows from~\cite{rossmann_limit_orbits}.  Update May 1: it seems the right place is Lemma B, and to go from that to the statement is a matter of chasing definitions and using the asymptotic cone. \textcolor{blue}{Update May 29: by Lemma B in~\cite{rossmann_limit_orbits}, if $\mathfrak{h}^+$ is the large Weyl chamber containing the HC parameter of~$\pi$, then $\lim_{x \to 0(\mathfrak{h}^+)} G\cdot x$ is a single orbit---where $\lim_{x \to 0(\mathfrak{h}^+)} G\cdot x$ is defined in Rossmann's paper. What we have to check is that the closure of this $\lim_{x \to 0(\mathfrak{h}^+)} G\cdot x$ contains $\WF(\pi)$. Now, I think that  the equivalence between conditions  (L1) and (L2) on page 2 of~\cite{rossmann_limit_orbits} easily implies that the closure of $\lim_{x \to 0(\mathfrak{h}^+)} G\cdot x$ contains the asymptotic cone of the orbit of the HC parameter, so the claim seems to follow from the relationship between $\WF(\pi)$ and the asymptotic cone.}
